### 2017-09-30 TF-vldb2018/subsec-Ginc.tex

We next propose \incd to handle $\Delta G$, followed the steps in Section~\ref{sec-dynamictopk}.
Given auxiliary structures $\tilde{M}(P,G)$ and \fb,
we show how to combine procedures \identifyaffball, \incmatch and \comb for computing match results for $P$ in $G \oplus \Delta G$.
%
\incmatch and \comb handle $\Delta G$ basically the same as $\Delta P$, so we mainly show how \identifyaffball identifies \affballsx \wrt $\Delta G$.

@@

\stitle{Remarks}. Note that the running time of \incd is determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$,
and hence the part for data updates in Theorem~\ref{thm-framework-inc} is proved. This also completes the proof of Theorem~\ref{thm-framework-inc}.

@@

We are now ready to provide algorithm \inc, integrating \incp and \incd, \revise{which are presented in Section~\ref{subsec-Qinc} and Section~\ref{subsec-Ginc}, respectively,} to process continuous pattern and data updates, separately and simultaneously.

@@

>>>>

We next propose \incd to handle $\Delta G$, following the framework in Section~\ref{subsec-framework}.
Given auxiliary structures $\tilde{M}(P,G)$ and \fb,
we put together procedures \identifyaffball, \incmatch and \comb for computing match results for $P$ in $G \oplus \Delta G$.
%
As procedures \incmatch and \comb handle $\Delta G$ basically the same as $\Delta P$, so we mainly show how \identifyaffball identifies \affballsx \wrt $\Delta G$.

@@

@@

We are now ready to provide algorithm \inc, integrating \incp and \incd, presented in Sections~\ref{subsec-Qinc} and~\ref{subsec-Ginc}, respectively, to process continuous pattern and data updates, separately and simultaneously.

@@

%\vspace{0.5ex}
\stitle{Remarks}. Note that (a) the running time of \incp is determined by $P$, $\Delta P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$, and
(b) the running time of \incd is determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
From these, we complete the proof of Theorem~\ref{thm-framework-inc}.

### 2017-09-30 TF-vldb2018/subsec-Qinc.tex

We present algorithm \incp to handle pattern updates $\Delta P$, followed the steps in Section~\ref{sec-dynamictopk}, and
an early return optimization technique for \incp.
%Note that for any $h$-fragmentation ${\cal P}_h$ of $P$, $|{\cal P}_h|$ = $|P|$.

@@

\sstab
(2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
Hence, there are no matches found in it and its inner balls.
\end{example}

@@

%\vspace{0.5ex}
\stitle{Remarks}. The running time of \incp is determined by $P$, $\Delta P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
Hence the part for pattern updates in Theorem~\ref{thm-framework-inc} is proved.

>>>>

We present algorithm \incp to handle pattern updates $\Delta P$, followed the steps in Section~\ref{subsec-framework}, and
an early return optimization technique for \incp.
%Note that for any $h$-fragmentation ${\cal P}_h$ of $P$, $|{\cal P}_h|$ = $|P|$.

@@

\sstab
(2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
So there no matches are found.
\end{example}

@@
